|

### 2020-12-10 04-Chp-Systematic-Review.Rmd
Fix fancy headers in template file and update other files

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:dara-quote)'}
Science knows it doesn't know everything; otherwise, it'd stop
```
(ref:dara-quote) --- Dara O'Briain

@@

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
knitr::read_chunk("R/Chp2-Systematic-Review.R")
```

@@

How to interpret agreement co-efficients is widely debated. Here we use guidelines based on a stricter interpreation of the Cohen's Kappa coefficient,[@mchugh2012] presented in Table \@ref(tab:gwettable).

@@

@@

Include here:

>>>>

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:dara-quote)'}
Science knows it doesn't know everything; otherwise, it'd stop
```

@@

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
knitr::read_chunk("R/Chp2-Systematic-Review.R")
knitr::opts_chunk$set(echo = FALSE)
```

@@

How to interpret agreement co-efficients is widely debated. Here we use guidelines based on a stricter interpreation of the Cohen's Kappa coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).

<!----------------------------------------------------------------------------->
``` {r gwet-setup, results="hide", message=FALSE}
```

```{r gwet-table, message=FALSE, results="asis"}
```
<!----------------------------------------------------------------------------->

@@

<!----------------------------------------------------------------------------->
``` {r chunkname_setup, results="hide", message=FALSE}
```

```{r chunkname_table, message=FALSE, results="asis"}
```
<!----------------------------------------------------------------------------->

@@

<!----------------------------------------------------------------------------->
Include here:

### 2020-12-10 index.Rmd
Fix fancy headers in template file and update other files

```{r create_chunk_options, include=FALSE, eval=knitr::is_latex_output()}
source('scripts_and_filters/create_chunk_options.R')
source("R/citations.R")
```

>>>>

```{r create_chunk_options, include=FALSE, eval=knitr::is_latex_output()}
source('scripts_and_filters/create_chunk_options.R')
source("R/helper.R")
source
```
